Greenhouse gas emissions model - making scenarios

### 2021-12-21 Scenarios_report.Rmd
adding some evaluations to the scenarios

```{r}
knitr::kable(read.table("data/farm_scenarios.csv", sep = ",", fileEncoding = "UTF-8-BOM",header=TRUE))

@@

uncertainty::varkernelslicerange(in_var = breed_res$y$pc_milk_yield,
                                 out_var = breed_res$y$pc_on_farm, 
                                 min_in_var = round(min(breed_res$y$pc_milk_yield)),
                                 max_in_var = round(max(breed_res$y$pc_milk_yield)), 
                                 xlab_vars = "Total emissions given milk yield range")

uncertainty::varkernelslicerange(in_var = GHG_simulation_scenarios$y$pc_milk_yield,
                        out_var = GHG_simulation_scenarios$y$pc_on_farm,
                                 min_in_var = round(min(GHG_simulation_scenarios$y$pc_milk_yield)),
                                 max_in_var = round(max(GHG_simulation_scenarios$y$pc_milk_yield)), 
                                 xlab_vars = "Total emissions given milk yield range")

@@

uncertainty::varkernelslicerange(in_var = nobull_res$y$pc_milk_yield,
                                 out_var = nobull_res$y$pc_on_farm, 
                                 min_in_var = round(min(nobull_res$y$pc_milk_yield,na.rm=TRUE)),
                                 max_in_var = round(max(nobull_res$y$pc_milk_yield,na.rm=TRUE)), 
                                 xlab_vars = "Total emissions given milk yield range")

uncertainty::varkernelslicerange(in_var = GHG_simulation_scenarios$y$pc_milk_yield,
                        out_var = GHG_simulation_scenarios$y$pc_on_farm,
                                 min_in_var = round(min(GHG_simulation_scenarios$y$pc_milk_yield)),
                                 max_in_var = round(max(GHG_simulation_scenarios$y$pc_milk_yield)), 
                                 xlab_vars = "Total emissions given milk yield range")

@@

uncertainty::varkernelslicerange(in_var = lessReplace_res$y$pc_milk_yield,
                                 out_var = lessReplace_res$y$pc_on_farm, 
                                 min_in_var = round(min(lessReplace_res$y$pc_milk_yield,na.rm=TRUE)),
                                 max_in_var = round(max(lessReplace_res$y$pc_milk_yield,na.rm=TRUE)), 
                                 xlab_vars = "Total emissions given milk yield range")

uncertainty::varkernelslicerange(in_var = GHG_simulation_scenarios$y$pc_milk_yield,
                        out_var = GHG_simulation_scenarios$y$pc_on_farm,
                                 min_in_var = round(min(GHG_simulation_scenarios$y$pc_milk_yield)),
                                 max_in_var = round(max(GHG_simulation_scenarios$y$pc_milk_yield)), 
                                 xlab_vars = "Total emissions given milk yield range")

>>>>

```{r}
knitr::kable(read.table("data/farm_scenarios.csv", sep = ",", fileEncoding = "UTF-8-BOM",header=TRUE)[,1:5])

@@

# uncertainty::varkernelslicerange(in_var = breed_res$y$pc_milk_yield,
#                                  out_var = breed_res$y$pc_on_farm, 
#                                  min_in_var = round(min(breed_res$y$pc_milk_yield)),
#                                  max_in_var = round(max(breed_res$y$pc_milk_yield)), 
#                                  xlab_vars = "Total emissions given milk yield range")
# 
# uncertainty::varkernelslicerange(in_var = GHG_simulation_scenarios$y$pc_milk_yield,
#                         out_var = GHG_simulation_scenarios$y$pc_on_farm,
#                                  min_in_var = round(min(GHG_simulation_scenarios$y$pc_milk_yield)),
#                                  max_in_var = round(max(GHG_simulation_scenarios$y$pc_milk_yield)), 
#                                  xlab_vars = "Total emissions given milk yield range")

@@

# uncertainty::varkernelslicerange(in_var = nobull_res$y$pc_milk_yield,
#                                  out_var = nobull_res$y$pc_on_farm, 
#                                  min_in_var = round(min(nobull_res$y$pc_milk_yield,na.rm=TRUE)),
#                                  max_in_var = round(max(nobull_res$y$pc_milk_yield,na.rm=TRUE)), 
#                                  xlab_vars = "Total emissions given milk yield range")
# 
# uncertainty::varkernelslicerange(in_var = GHG_simulation_scenarios$y$pc_milk_yield,
#                         out_var = GHG_simulation_scenarios$y$pc_on_farm,
#                                  min_in_var = round(min(GHG_simulation_scenarios$y$pc_milk_yield)),
#                                  max_in_var = round(max(GHG_simulation_scenarios$y$pc_milk_yield)), 
#                                  xlab_vars = "Total emissions given milk yield range")

@@

# uncertainty::varkernelslicerange(in_var = lessReplace_res$y$pc_milk_yield,
#                                  out_var = lessReplace_res$y$pc_on_farm, 
#                                  min_in_var = round(min(lessReplace_res$y$pc_milk_yield,na.rm=TRUE)),
#                                  max_in_var = round(max(lessReplace_res$y$pc_milk_yield,na.rm=TRUE)), 
#                                  xlab_vars = "Total emissions given milk yield range")
# 
# uncertainty::varkernelslicerange(in_var = GHG_simulation_scenarios$y$pc_milk_yield,
#                         out_var = GHG_simulation_scenarios$y$pc_on_farm,
#                                  min_in_var = round(min(GHG_simulation_scenarios$y$pc_milk_yield)),
#                                  max_in_var = round(max(GHG_simulation_scenarios$y$pc_milk_yield)), 
#                                  xlab_vars = "Total emissions given milk yield range")

# Comparing the scenarios

Below we compare the density distributions for the scenarios. This required loading some helper functions that contain modified versions of some functions from the `uncertainty` package (`multi_data_varkernelslicerange` and `data_varkernelslicerange`).

```{r uncertainty_evaluation_functions, include=FALSE}
# Generate the GHG emissions function 
source("uncertainty_evaluation.R", local = knitr::knit_global())
```

The plot below shows that in terms of per-capita emissions, the difference between the scenarios is not impressive.

```{r}
per_capita_scenarios<-list(list(scenario="Baseline",
                     in_var=GHG_simulation_scenarios$y$pc_milk_yield,
                     out_var=GHG_simulation_scenarios$y$pc_on_farm),
                list(scenario="Less male replacement",
                     in_var=lessReplace_res$y$pc_milk_yield,
                     out_var=lessReplace_res$y$pc_on_farm),
                list(scenario="No bulls",
                     in_var=nobull_res$y$pc_milk_yield,
                     out_var=nobull_res$y$pc_on_farm),
                list(scenario="Breed upgrade",
                     in_var=breed_res$y$pc_milk_yield,
                     out_var=breed_res$y$pc_on_farm))

per_capita_emissions<-multi_data_varkernelslicerange(per_capita_scenarios)

library(ggplot2)

ggplot(data = per_capita_emissions$slice_values, aes(x = y, y = z, color = scenario)) +
  geom_line() + theme_bw(base_size = 12) +
  xlab(expression(Per~capita~emissions~(kg~CO[2]-eq~year^-1))) +
  ylab("Density") +
  ggtitle("Per capita emissions") +
  scale_color_discrete(name = "Scenario")

We can also look at the distribution of emissions per kg of milk yield. The plot below shows the cumulative probability distribution for this metric. The differences are a bit more visible here, but still fairly minor.

```{r}

ghg_per_milk <-
  rbind(
    data.frame(
      scenario = "Baseline",
      milk_yield = GHG_simulation_scenarios$y$pc_milk_yield,
      GHG = GHG_simulation_scenarios$y$pc_on_farm
    ),data.frame(
      scenario = "Less male replacement",
      milk_yield = lessReplace_res$y$pc_milk_yield,
      GHG = lessReplace_res$y$pc_on_farm
    ),data.frame(
      scenario = "No bulls",
      milk_yield = nobull_res$y$pc_milk_yield,
      GHG = nobull_res$y$pc_on_farm
    ),data.frame(
      scenario = "Breed upgrade",
      milk_yield = breed_res$y$pc_milk_yield,
      GHG = breed_res$y$pc_on_farm
    ))
ghg_per_milk[,"ghg_per_milk"]<-ghg_per_milk$GHG/ghg_per_milk$milk_yield

ggplot(data = ghg_per_milk, aes(x = ghg_per_milk, color = scenario)) +
  stat_ecdf() + xlim(0, 10) + theme_bw(base_size = 12) + ggtitle("Emissions per kg of milk (truncated at 10 kg)") + xlab(expression(Emissions~per~kg~milk~(kg~CO[2]-eq~year^-1))) + ylab("Cumulative probability")
